Global adjoint tomography -- Model GLAD-M25 \\ Supplementary Material

### 2020-05-17 supplementary_material.tex
fix psf figure caption issue

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/easter.png}
  \caption{\small{PSF test for Easter Island.
  A 300~km diameter negative Gaussian anomaly is placed at a depth of 2,500~km beneath Easter Island.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.}}
  \label{fig:psf_easter}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/afar.png}
  \caption{\small{PSF test for Afar.
    A 400~km diameter negative Gaussian anomaly is placed at a depth of 2,000~km beneath Afar.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
  }}
  \label{fig:psf_afar}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/su.png}
  \caption{\small{PSF test for Sumatra.
    A 200~km diameter positive Gaussian anomaly is placed at a depth of 900~km beneath Sumatra.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
  }}
  \label{fig:psf_su}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/usa_east.png}
  \caption{\small{PSF test underneath the eastern United States.
    A 250~km diameter positive Gaussian anomaly is placed at a depth of 1500~km beneath the eastern US.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
  }}
  \label{fig:psf_usa_east}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.95\textwidth]{figures/psf/psf-1200km.pdf}
  \caption{\small{Patterned PSF test at a depth of 1,200~km,
  where the model is isotropic.
    An alternating positive and negative pattern of 100~km diameter Gaussian anomalies in shear wavespeed is placed at a depth of 1,200~km.
  Left: input pattern for~$\beta$.
  Middle: recovered pattern for~$\beta$.
  Right: tradeoff with bulk sound speed~$c$.
  We conclude that there is little tradeoff between~$\beta$ and~$c$, and that the pattern at this mid-mantle depth is reasonably well recovered, both in terms of geometry and in terms of strength.
  }}
  \label{fig:patern1200}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/easter.png}
  \caption{\small{PSF test for Easter Island.
  A 300~km diameter negative Gaussian anomaly is placed at a depth of 2,500~km beneath Easter Island.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta$ and~$c$.
  }}
  \label{fig:psf_easter}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/afar.png}
  \caption{\small{PSF test for Afar.
    A 400~km diameter negative Gaussian anomaly is placed at a depth of 2,000~km beneath Afar.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta$ and~$c$.
  }}
  \label{fig:psf_afar}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/su.png}
  \caption{\small{PSF test for Sumatra.
    A 200~km diameter positive Gaussian anomaly is placed at a depth of 900~km beneath Sumatra.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta$ and~$c$.
  }}
  \label{fig:psf_su}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/usa_east.png}
  \caption{\small{PSF test underneath the eastern United States.
    A 250~km diameter positive Gaussian anomaly is placed at a depth of 1500~km beneath the eastern US.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta$ and~$c$.
  }}
  \label{fig:psf_usa_east}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.75\textwidth]{figures/psf/psf-1200km.pdf}
  \caption{\small{Patterned PSF test at a depth of 1,200~km,
  where the model is isotropic.
    An alternating positive and negative pattern of 100~km diameter Gaussian anomalies in shear wavespeed is placed at a depth of 1,200~km.
  Top: input pattern for~$\beta$.
  Middle: recovered pattern for~$\beta$.
  Bottom: tradeoff with bulk sound speed~$c$.
  We conclude that there is little tradeoff between~$\beta$ and~$c$, and that the pattern at this mid-mantle depth is reasonably well recovered, both in terms of geometry and in terms of strength.
  }}
  \label{fig:patern1200}
\end{figure}
